Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-08-10 Multiresolution_framework/ltx/manuscript.tex
Some further changes in Section 6.

\ken{Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted. A simpler, more parsimonious model might be unable to capture the full detail of the system behaviour but usually results in accurate and computationally efficient estimates. On the other hand, more complex and higher dimensional descriptions require computationally costly methods and less accurate estimates.}

\ken{Thus, to demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear. Note that by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period. This allows for the adoption of the EM algorithm and thus results in computationally efficient and accurate estimates. As a result, any loss in model detail may be offset by the estimation accuracy.}

>>>>

\ken{Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted. Such a choice is usually based on the principle of parsimony \cite{Illfindit}, that is; the simplest model capable of capturing the system behaviour of interest is chosen. Such a choice in favour of a simpler model has the added advantages of a smaller parameter space and therefore more accurate estimates and computationally efficient methods.}

\ken{To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear. Note that by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period. This allows for the adoption of the EM algorithm and thus results in computationally efficient and accurate estimates. As a result, any loss in model detail may be offset by the estimation accuracy.}
